Location and Scale-Invariant Power Transformations for Transforming Data to Normality

### 2025-10-29 manuscript_latex/manuscript.tex
Updated figures from main manuscript.

{\centering \includegraphics{manuscript_files/figure-latex/decreased-normality-1}

@@

{\centering \includegraphics{manuscript_files/figure-latex/weighting-functions-1}

@@

{\centering \includegraphics{manuscript_files/figure-latex/shifted-distributions-1}

@@

{\centering \includegraphics{manuscript_files/figure-latex/empirical-central-normality-combined-1}

@@

{\centering \includegraphics{manuscript_files/figure-latex/empirical-central-normality-error_rate-1}

@@

{\centering \includegraphics{manuscript_files/figure-latex/empirical-central-normality-examples-1}

@@

{\centering \includegraphics{manuscript_files/figure-latex/experimental-results-invariance-1}

@@

{\centering \includegraphics{manuscript_files/figure-latex/experimental-results-outlier-robustness-1}

@@

{\centering \includegraphics{manuscript_files/figure-latex/marginal-effect-plot-1}

>>>>

{\centering \includegraphics[width=1\linewidth]{figure-1}

@@

{\centering \includegraphics[width=1\linewidth]{figure-2}

@@

{\centering \includegraphics[width=1\linewidth]{figure-3}

@@

{\centering \includegraphics[width=1\linewidth]{figure-4}

@@

{\centering \includegraphics[width=1\linewidth]{figure-5}

@@

{\centering \includegraphics[width=1\linewidth]{figure-6}

@@

{\centering \includegraphics[width=1\linewidth]{figure-7}

@@

{\centering \includegraphics[width=1\linewidth]{figure-8}

@@

{\centering \includegraphics[width=1\linewidth]{figure-9}
